\sysfull

### 2017-08-09 paper/intro.tex
Section I revised

\todo{This is the main pitch statement: we should all agree that this is what \sys does}{All} In this work we develop {\bf \sys}: a new programming and execution model that efficiently executes tasks and avoids non-termination across a range of energy buffer sizes, without burdening the programmer. To accomplish this goal, \sys introduces three new capabilities:

\begin{itemize}
	\item {\bf Automatic task compilation:} \sys's compiler transforms arbitrary C code into a graph of tasks that reflects the original program's control- and data-flow constraints. The compiler identifies data shared by multiple of the newly created tasks and instruments reads and writes of those data so that \sys's memory virtualization mechanism keeps those data consistent. \sys complier effectively circumvents the need for labour-intensive manual task generation of the state-of-the-art solutions~\cite{chain,alpaca}. \todo{Elaborate on this more and provide numerical results}{Przemek}
	%
	\item {\bf Dynamic task coalescing:} \sys's memory virtualization mechanism uses SRAM as working memory, which \sys dynamically populates with pages of data from FRAM on demand during a task's execution. When a task ends, \sys commits dirty pages to FRAM using efficient DMA block copies, ensuring task atomicity and memory consistency. \todo{Once paging is fully implemented--update the paragraph}{Przemek}\todo{Provide numerical results for this section}{Przemek}
	%
	\item {\bf Volatile memory virtualization:} \sys's task coalescing mechanism executes multiple statically defined tasks together as a single dynamic task. A programmer can specify small tasks that will execute on a device with a small energy buffer. Coalescing tasks allows running the same tasks on a device with a larger energy buffer, while avoiding run time overheads associated with ending one task and beginning another.\todo{Provide numerical results for this section}{Przemek}
\end{itemize}

@@

%\todo{I think these are all much too long, given the depth of the intro and background already. I suggest we cut to the barest minimum.}

>>>>

In this work we develop {\bf \sys}: a new programming and execution model that efficiently executes tasks and avoids non-termination across a range of energy buffer sizes, without burdening the programmer. To accomplish this goal, \sys introduces three new capabilities:

\begin{itemize}
	\item {\bf Automatic task compilation:} \sys's compiler transforms arbitrary C code into a graph of tasks that reflects the original program's control- and data-flow constraints. The compiler identifies data shared by multiple of the newly created tasks and instruments reads and writes of those data so that \sys's memory virtualization mechanism keeps those data consistent. \sys complier effectively circumvents the need for labour-intensive manual task generation of the state-of-the-art solutions~\cite{chain,alpaca} (spanning hours of programmer work) completing task compilation in the order of seconds.
	%
	\item {\bf Dynamic task coalescing:} \sys's task coalescing mechanism executes multiple statically-derived tasks together as a single dynamic task. A programmer or compiler can specify small tasks that will execute on a device with a small energy buffer. Coalescing tasks allows running the same tasks on a device with a larger energy buffer, while avoiding run time overheads associated with ending one task and beginning another.\todo{Provide numerical results for this section}{Przemek}
	%
	\item {\bf Volatile memory virtualization:} \sys's memory virtualization mechanism uses SRAM as working memory, which \sys dynamically populates with pages of data from FRAM on demand during a task's execution. When a task ends, \sys commits dirty pages to FRAM using efficient DMA block copies, ensuring task atomicity and memory consistency. \todo{Once paging is fully implemented--update the paragraph}{Przemek}\todo{Provide numerical results for this section}{Przemek}
\end{itemize}

@@
